Extended Data

### 2021-09-17 doc/manuscript/Dow_Extended_Data.Rmd
knit in map

## figure captions
growth_curves_all_caption  <- " Extended Data Figure 2 | Growth trajectories for ring- and diffuse-porous trees, as both relative and cumulative fractions of total annual growth. Each line represents one year's growth for a given tree, fit with McMahon model. " #needs wordsmithing!!!

@@

## (PLACEHOLDER FOR MAP OF STUDY SITES -- [GITHUB ISSUE #54](https://github.com/EcoClimLab/growth_phenology/issues/54))

>>>>

## figure captions

map_caption <- "**Extended Data Figure 1 | Map of sampling locations of tree-ring chronologies analyzed in this study.** Sites are colored by the xylem porosity type of species sampled: ring poroous (RP), diffuse porous (DP), or both. Sampling details are provided in **SI TBALE NAME**" #needs attention!!!

growth_curves_all_caption  <- " Extended Data Figure 2 | Growth trajectories for ring- and diffuse-porous trees, as both relative and cumulative fractions of total annual growth. Each line represents one year's growth for a given tree, fit with McMahon model. " #needs wordsmithing!!!

@@

![`r map_caption`](tables_figures/chronology_map.png)
